Plots and tables summarizing results of Poisson simulations

### 2019-11-14 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

For each combination of test function and intensity range, we
simulated 100 data sets. In the plots and tables below, we summarize
the error (MISE) in the estimates computed in the 100 data sets from
each simulation setting.

The plots for the "Bursts" simulations shown below were also included
in the manuscript.

@@

```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
m                  <- length(mise.ash.s.1)
method.labels      <- c("Haar-Fisz","BMSM","SMASH")
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
                                     mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
pdat128 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

@@

```{r angles-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.ang.1   <- colMeans(rbind(mise.hf.ti.r.4.ang.1,
                                       mise.hf.ti.r.5.ang.1,
                                       mise.hf.ti.r.6.ang.1,
					  				   mise.hf.ti.r.7.ang.1))
mise.hf.ti.r.ang.8   <- colMeans(rbind(mise.hf.ti.r.4.ang.8,
 									   mise.hf.ti.r.5.ang.8,
                                       mise.hf.ti.r.6.ang.8,
                                       mise.hf.ti.r.7.ang.8))
mise.hf.ti.r.ang.128 <- colMeans(rbind(mise.hf.ti.r.4.ang.128,
                                       mise.hf.ti.r.5.ang.128,
                                       mise.hf.ti.r.6.ang.128,
									   mise.hf.ti.r.7.ang.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.ang.1,mise.BMSM.ang.1,mise.ash.ang.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.ang.8,mise.BMSM.ang.8,mise.ash.ang.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.ang.128,mise.BMSM.ang.128,mise.ash.ang.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

@@

```{r heavisine-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.hs.1   <- colMeans(rbind(mise.hf.ti.r.4.hs.1,
                                      mise.hf.ti.r.5.hs.1,
                                      mise.hf.ti.r.6.hs.1,
						  			  mise.hf.ti.r.7.hs.1))
mise.hf.ti.r.hs.8   <- colMeans(rbind(mise.hf.ti.r.4.hs.8,
                                      mise.hf.ti.r.5.hs.8,
                                      mise.hf.ti.r.6.hs.8,
							  		  mise.hf.ti.r.7.hs.8))
mise.hf.ti.r.hs.128 <- colMeans(rbind(mise.hf.ti.r.4.hs.128,
                                      mise.hf.ti.r.5.hs.128,
                                      mise.hf.ti.r.6.hs.128,
									  mise.hf.ti.r.7.hs.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.hs.1,mise.BMSM.hs.1,mise.ash.hs.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.hs.8,mise.BMSM.hs.8,mise.ash.hs.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.hs.128,mise.BMSM.hs.128,mise.ash.hs.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

@@

```{r bursts-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.bur.1   <- colMeans(rbind(mise.hf.ti.r.4.bur.1,
                                       mise.hf.ti.r.5.bur.1,
                                       mise.hf.ti.r.6.bur.1,
						  			   mise.hf.ti.r.7.bur.1))
mise.hf.ti.r.bur.8   <- colMeans(rbind(mise.hf.ti.r.4.bur.8,
                                       mise.hf.ti.r.5.bur.8,
                                       mise.hf.ti.r.6.bur.8,
									   mise.hf.ti.r.7.bur.8))
mise.hf.ti.r.bur.128 <- colMeans(rbind(mise.hf.ti.r.4.bur.128,
                                       mise.hf.ti.r.5.bur.128,
                                       mise.hf.ti.r.6.bur.128,
									   mise.hf.ti.r.7.bur.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.bur.1,mise.BMSM.bur.1,mise.ash.bur.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.bur.8,mise.BMSM.bur.8,mise.ash.bur.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.bur.128,mise.BMSM.bur.128,mise.ash.bur.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

@@

```{r cb-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.cb.1   <- colMeans(rbind(mise.hf.ti.r.4.cb.1,
                                      mise.hf.ti.r.5.cb.1,
                                      mise.hf.ti.r.6.cb.1,
			  						  mise.hf.ti.r.7.cb.1))
mise.hf.ti.r.cb.8   <- colMeans(rbind(mise.hf.ti.r.4.cb.8,
                                      mise.hf.ti.r.5.cb.8,
                                      mise.hf.ti.r.6.cb.8,
									  mise.hf.ti.r.7.cb.8))
mise.hf.ti.r.cb.128 <- colMeans(rbind(mise.hf.ti.r.4.cb.128,
                                      mise.hf.ti.r.5.cb.128,
                                      mise.hf.ti.r.6.cb.128,
									  mise.hf.ti.r.7.cb.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.1,mise.BMSM.cb.1,mise.ash.cb.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.8,mise.BMSM.cb.8,mise.ash.cb.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.cb.128,mise.BMSM.cb.128,mise.ash.cb.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

@@

```{r bumps-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.b.1   <- colMeans(rbind(mise.hf.ti.r.4.b.1,
                                     mise.hf.ti.r.5.b.1,
                                     mise.hf.ti.r.6.b.1,
                                     mise.hf.ti.r.7.b.1))
mise.hf.ti.r.b.8   <- colMeans(rbind(mise.hf.ti.r.4.b.8,
                                     mise.hf.ti.r.5.b.8,
                                     mise.hf.ti.r.6.b.8,
									 mise.hf.ti.r.7.b.8))
mise.hf.ti.r.b.128 <- colMeans(rbind(mise.hf.ti.r.4.b.128,
									 mise.hf.ti.r.5.b.128,
									 mise.hf.ti.r.6.b.128,
									 mise.hf.ti.r.7.b.128))
pdat.hf.1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.1,
                                         BMSM        = mise.BMSM.b.1,
		  						         SMASH       = mise.ash.b.1))
pdat.hf.8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.8,
                                         BMSM        = mise.BMSM.b.8,
				   				         SMASH       = mise.ash.b.8))
pdat.hf.128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.128,
                                         BMSM        = mise.BMSM.b.128,
									     SMASH       = mise.ash.b.128))
create.violin.plots(pdat.hf.1,pdat.hf.8,pdat.hf.128)
```

>>>>

For each combination of test function and intensity range, we
simulated 100 data sets. In the plots and tables below, we summarize
the error (MISE) in the estimates computed in the 100 data sets from
each simulation setting. A final summary of all the simulations is
shown at the end.

The plots shown below for the "Bursts" simulations, as well as the bar
plots summarizing all the Poisson simulations, were included in the
manuscript.

@@

```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
                                     mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
pdat.s1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.s.1,
                                       "BMSM"      = mise.BMSM.s.1,
	  						           "SMASH"     = mise.ash.s.1))
pdat.s8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.s.8,
                                       "BMSM"      = mise.BMSM.s.8,
	  						           "SMASH"     = mise.ash.s.8))
pdat.s128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.s.128,
                                       "BMSM"      = mise.BMSM.s.128,
	  						           "SMASH"     = mise.ash.s.128))
create.violin.plots(pdat.s1,pdat.s8,pdat.s128)
```

@@

```{r angles-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.ang.1   <- colMeans(rbind(mise.hf.ti.r.4.ang.1,
                                       mise.hf.ti.r.5.ang.1,
                                       mise.hf.ti.r.6.ang.1,
					  				   mise.hf.ti.r.7.ang.1))
mise.hf.ti.r.ang.8   <- colMeans(rbind(mise.hf.ti.r.4.ang.8,
 									   mise.hf.ti.r.5.ang.8,
                                       mise.hf.ti.r.6.ang.8,
                                       mise.hf.ti.r.7.ang.8))
mise.hf.ti.r.ang.128 <- colMeans(rbind(mise.hf.ti.r.4.ang.128,
                                       mise.hf.ti.r.5.ang.128,
                                       mise.hf.ti.r.6.ang.128,
									   mise.hf.ti.r.7.ang.128))
pdat.ang1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.ang.1,
                                         "BMSM"      = mise.BMSM.ang.1,
	  						             "SMASH"     = mise.ash.ang.1))
pdat.ang8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.ang.8,
                                         "BMSM"      = mise.BMSM.ang.8,
	  						             "SMASH"     = mise.ash.ang.8))
pdat.ang128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.ang.128,
                                         "BMSM"      = mise.BMSM.ang.128,
	  						             "SMASH"     = mise.ash.ang.128))
create.violin.plots(pdat.ang1,pdat.ang8,pdat.ang128)
```

@@

```{r heavisine-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.hs.1   <- colMeans(rbind(mise.hf.ti.r.4.hs.1,
                                      mise.hf.ti.r.5.hs.1,
                                      mise.hf.ti.r.6.hs.1,
						  			  mise.hf.ti.r.7.hs.1))
mise.hf.ti.r.hs.8   <- colMeans(rbind(mise.hf.ti.r.4.hs.8,
                                      mise.hf.ti.r.5.hs.8,
                                      mise.hf.ti.r.6.hs.8,
							  		  mise.hf.ti.r.7.hs.8))
mise.hf.ti.r.hs.128 <- colMeans(rbind(mise.hf.ti.r.4.hs.128,
                                      mise.hf.ti.r.5.hs.128,
                                      mise.hf.ti.r.6.hs.128,
									  mise.hf.ti.r.7.hs.128))
pdat.hs1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.hs.1,
                                        "BMSM"      = mise.BMSM.hs.1,
	  						            "SMASH"     = mise.ash.hs.1))
pdat.hs8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.hs.8,
                                        "BMSM"      = mise.BMSM.hs.8,
	  						            "SMASH"     = mise.ash.hs.8))
pdat.hs128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.hs.128,
                                        "BMSM"      = mise.BMSM.hs.128,
	  						            "SMASH"     = mise.ash.hs.128))
create.violin.plots(pdat.hs1,pdat.hs8,pdat.hs128)
```

@@

```{r bursts-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.bur.1   <- colMeans(rbind(mise.hf.ti.r.4.bur.1,
                                       mise.hf.ti.r.5.bur.1,
                                       mise.hf.ti.r.6.bur.1,
						  			   mise.hf.ti.r.7.bur.1))
mise.hf.ti.r.bur.8   <- colMeans(rbind(mise.hf.ti.r.4.bur.8,
                                       mise.hf.ti.r.5.bur.8,
                                       mise.hf.ti.r.6.bur.8,
									   mise.hf.ti.r.7.bur.8))
mise.hf.ti.r.bur.128 <- colMeans(rbind(mise.hf.ti.r.4.bur.128,
                                       mise.hf.ti.r.5.bur.128,
                                       mise.hf.ti.r.6.bur.128,
									   mise.hf.ti.r.7.bur.128))
pdat.bur1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.bur.1,
                                         "BMSM"      = mise.BMSM.bur.1,
	  						             "SMASH"     = mise.ash.bur.1))
pdat.bur8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.bur.8,
                                         "BMSM"      = mise.BMSM.bur.8,
	  						             "SMASH"     = mise.ash.bur.8))
pdat.bur128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.bur.128,
                                         "BMSM"      = mise.BMSM.bur.128,
	  						             "SMASH"     = mise.ash.bur.128))
create.violin.plots(pdat.bur1,pdat.bur8,pdat.bur128)
```

@@

```{r cb-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.cb.1   <- colMeans(rbind(mise.hf.ti.r.4.cb.1,
                                      mise.hf.ti.r.5.cb.1,
                                      mise.hf.ti.r.6.cb.1,
			  						  mise.hf.ti.r.7.cb.1))
mise.hf.ti.r.cb.8   <- colMeans(rbind(mise.hf.ti.r.4.cb.8,
                                      mise.hf.ti.r.5.cb.8,
                                      mise.hf.ti.r.6.cb.8,
									  mise.hf.ti.r.7.cb.8))
mise.hf.ti.r.cb.128 <- colMeans(rbind(mise.hf.ti.r.4.cb.128,
                                      mise.hf.ti.r.5.cb.128,
                                      mise.hf.ti.r.6.cb.128,
									  mise.hf.ti.r.7.cb.128))
pdat.cb1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.cb.1,
                                        "BMSM"      = mise.BMSM.cb.1,
	  						            "SMASH"     = mise.ash.cb.1))
pdat.cb8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.cb.8,
                                        "BMSM"      = mise.BMSM.cb.8,
	  						            "SMASH"     = mise.ash.cb.8))
pdat.cb128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.cb.128,
                                        "BMSM"      = mise.BMSM.cb.128,
	  						            "SMASH"     = mise.ash.cb.128))
create.violin.plots(pdat.cb1,pdat.cb8,pdat.cb128)
```

@@

```{r bumps-violin-plots, fig.height=3.25, fig.width=10}
mise.hf.ti.r.b.1   <- colMeans(rbind(mise.hf.ti.r.4.b.1,
                                     mise.hf.ti.r.5.b.1,
                                     mise.hf.ti.r.6.b.1,
                                     mise.hf.ti.r.7.b.1))
mise.hf.ti.r.b.8   <- colMeans(rbind(mise.hf.ti.r.4.b.8,
                                     mise.hf.ti.r.5.b.8,
                                     mise.hf.ti.r.6.b.8,
									 mise.hf.ti.r.7.b.8))
mise.hf.ti.r.b.128 <- colMeans(rbind(mise.hf.ti.r.4.b.128,
									 mise.hf.ti.r.5.b.128,
									 mise.hf.ti.r.6.b.128,
									 mise.hf.ti.r.7.b.128))
pdat.b1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.1,
                                       "BMSM"      = mise.BMSM.b.1,
	  						           "SMASH"     = mise.ash.b.1))
pdat.b8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.8,
                                       "BMSM"      = mise.BMSM.b.8,
				   				       "SMASH"     = mise.ash.b.8))
pdat.b128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.128,
                                       "BMSM"      = mise.BMSM.b.128,
									   "SMASH"     = mise.ash.b.128))
create.violin.plots(pdat.b1,pdat.b8,pdat.b128)
```
